The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

###Research Question  
Drawing a comparison between Portugal, Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - the degree of reliance on positive reinforcement in teaching - affect the rate of entrepreneurship in each country?

@@

The specific variables to trace this potential causal chain still need to be determined.

####Estimation Strategy  
The estimation strategy will consist of using cross-sectional data about Portugal, Sweden, France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.

@@

The explanatory variables will be the sense of belonging to the group as defined by OECD [Program for International Student Assessment (PISA)](http://www.oecd.org/pisa/) (Data from 2012), the sense of individuality as an index constructed from [World Value Survey](http://www.worldvaluessurvey.org/wvs.jsp) items (Data from 2005 /2006), the degree of self confidence as an index again gathered from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).

@@

The first step will be to see what the different behavioural and cultural patterns are in each country as observed among students. The differences observed may require some cultural explanations, including explanations regarding the type of welfare state in the given country.

@@

Our main hypothesis is that the more culturally group-oriented and the more self-confident a population is, the higher entrepreneurship in that country will be.

>>>>

###Research Question  
Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - the degree of reliance on positive reinforcement in teaching - affect the rate of entrepreneurship in each country?

@@

####Estimation Strategy  
The estimation strategy will consist of using cross-sectional data about France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.

@@

The key explanatory variable will be the degree of self confidence as an index that we will compute from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).

@@

The first step will be to see if, regarding self-confidence, different patterns can be observed in each country. In which case, we may need to call on cultural explanations.

@@

Our main hypothesis is that the more self-confident a population is on average, the higher entrepreneurship in that country will be.
